Joint Power Allocation and Network Slicing in an Open RAN System \vspace{-.1cm}

### 2020-04-19 Latex/tex/pr.tex
last
ns

\begin{abstract}
Many major telecommunication companies confirmed the unification of the xRAN Group with the C-RAN Alliance to establish a more flexible and openness radio access network which is the Open-RAN
(ORAN) for the fifth generation of wireless technology. To increase energy efficiency and optimize the allocation of resources, Network Slicing (NS) is considered as the best method for the fifth generation (5G) in order to virtualize the common physical network into several logical end-to-end networks. Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to-end network. In this paper, we elaborate joint NS in RAN and Core of ORAN system to investigate the power
of each User Equipment (UE), map slices to services and also map physical Data Centers (DC) to slices to jointly maximize energy efficiency and minimize consumption power of RUs and the cost of  physical resources in a downlink channel. The problem is formulated as a mixed-integer optimization problem that can be decomposed into two independent sub-problems.
Heuristic algorithms are proposed to each of sub-problems in order to map slices to services, optimize power consumption and map slices to physical resources to minimize the cost of total DCs simultaneously.
\end{abstract}

\begin{IEEEkeywords}
ORAN, Network Slicing, Energy Efficiency, Data Center (DC)
\end{IEEEkeywords}

@@

ORAN virtualizes the elements of the radio access networks, separate them and define appropriate open interfaces for connection of these elements. Moreover, ORAN uses machine learning techniques to develop smarter RAN layers in its architecture. In an innovative ORAN system, the programmable RAN software is decoupled from hardware \cite{oran1}. Open interface is one of the most crucial properties for ORAN to enable mobile network operators (MNOs) to define their own services.
The concept of software defined network (SDN), which is the separation of control plane from user plane, is deployed in an intelligent ORAN architecture. Moreover, this separation promotes RRM to use non-realtime (RT) and near-realtime (NRT) RAN Intelligent Controller (RIC).
In the ORAN architecture, distributed unit (DU) is a logical node having RLC/MAC/High-PHY layer.
Moreover, central unit (CU) is a logical node having RRC, SDAP and PDCP. Also, radio unit (RU) is a logical node having LOW-PHY layer and
RF processing \cite{oranpaper}.
ORAN introduces interfaces such as open fronthaul interface that connects DU and RU (i.e., E2 interface), and an A1 interface between orchestration/NMS layer containing the non-real-time RIC (RIC non-RT) function and the eNB/gNB containing the near-real-time RIC (RIC near-RT) function.

To evolve servicing in 5G networks, separation of elements of software and hardware of network is employed and referred as network functions virtualization (NFV). Virtual network function (VNF) are functional blocks of the system in this case. 5G networks are expected to host several services with different requirements simultaneously. Network slicing is considered as a solution for such demand. A network slice is a logical end-to-end network which provide service with specific requirements. Multiple network slices run on the same physical network infrastructure which are managed and operate independently \cite{lee2018dynamic}. Slicing can be defined for the RAN, for the core network or both of these networks \cite{ns1}.

Based on their type of request, UEs are classified into various services, where UEs in the same service have similar service requests. In addition, each service is mapped to one or more slices based on the resources of the slices. Each VNF of the ORAN is mapped to one or some virtual machines (VMs) in the data center. For simplicity of analysis and without loss of generality, we assume a VNF is mapped to one VM and requires specific physical resources including storage, memory, and processing \cite{frdl,luong2018novel,luong2018novel1}.

%The compression of messages passed through the fronthaul link due to the limited capacity of these links is considered in \cite{simeone2016cloud,1111}.
In \cite{oranT},  the evolution of RAN in the  5G network is described. The architecture of C-RAN and X-RAN is expressed and development of the ORAN from C-RAN and X-RAN is explained. Also requirements of the network in terms of capacity and latency is taken into account.
In \cite{oran12},  the ORAN architecture is studied. The eight work groups is discussed including: focus areas of ORAN alliance which contains use-cases, overall architecture,  open interfaces, and  the virtualization and modularization of hardware and software. To the best of our knowledge, there is not work in the literature to model ORAN systems.

@@

In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The RAN is divided into three layers including RU, DU, and CU with open interfaces. DU and CU are running on general purpose data centers. UEs are divided to different services according to their service requirements. RAN resources are decoupled to slices to provide requirements of services. Optimal power allocation and joint mapping of slices to services are applied. In addition, mapping slices to physical resources is taken to account. The contribution of the paper is expressed as follow:
\begin{itemize}
\item In this paper, joint network slicing and resource allocation is considered in an end to end ORAN system.
\item UEs are categorized into different class of services based on their service requirements. RAN which contains RUs, PRBs, and VNFs ,in the two layer of processing, are classified into different group of slices.
\item The problem is decomposed into two independent sub-problems.
\item Heuristic algorithms are applied for the sub-problems to efficiently obtain the solution.
\end{itemize}

The rest of the paper is organized as follows. In Section \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical data center resources is expressed. Then, problem statement is explained and decomposed into two independent sub-problems.
In Section \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In Section \ref{simul}, numerical results are provided for the problem.

@@

single-antenna user equipments (UEs) that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ physical resource blocks (PRBs), one DU and one CU that contains VNFs.
Slices can have shared resources. All RUs in a slice, that is mapped to a service, transmit signals cooperatively to all the UEs in a specific service \cite{motalleb2017optimal,mimoCran}. Each RU $r \in \{1,2,...,R \}$ is mapped to a DU via an optical fiber link with limited fronthaul capacity.

@@

Also, RUs and PRBs can serve more than one slices.

@@

Mean delay of each slice is

@@

where, $P_r^{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RUs in all slices. Also, $\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the toal rates of all UEs applied for all types of services.

@@

\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{Y} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\psi_{tot}(\boldsymbol{Y})} \\

@@

@@

\If {conditions \eqref{c11}, \eqref{c12}, \eqref{c13} and \eqref{c14} is not applied}

@@

\caption{Plecement of Physical resources into Virtual resources}\label{alg3}

@@

In this section, simulation and numerical results for the main problem are depicted.

@@

 Maxmimun transmit Power of each RU & 40dBm \\

@@

In Fig. \ref{fig:f1a}, energy efficiency is depicted for two different numbers of services with the different mean number of UEs in each service (the parameters for simulation listed in table \ref{table:1a}). The optimal method is obtained by using MOSEK toolbox to obtain $\boldsymbol{A}$ and CVX toolbox to obtain $\boldsymbol{P}$ and iteratively updates $\boldsymbol{A}$, $\eta$ and $\boldsymbol{P}$. The optimal method is $0.1$ bits/J/Hz better than the proposed method for $V = 6$ and $E[U_v] = 10$, and also, $0.09$ bits/J/Hz better than the proposed method for $V = 3$ and, $E[U_v] = 10$. As it is shown, the Energy Efficiency is increased as a mean number of UEs rises.

@@

In Fig. \ref{fig:f1}, the ratio of admitted slices is demonstrated for two different numbers of DCs with the different number of slices (the parameters for simulation listed in table \ref{table:1} and also we set $w_C = 320$, $w_S = 100$, $w_M =1$). In this simulation, the second term of \eqref{eqpsi}, is important and the designed parameter $\nu$ is supposed to be high.

@@

The proposed method is based on Algorithm \ref{alg3}, and the optimal method is done by the MOSEK toolbox.

@@

In Fig. \ref{fig:f2}, the normalized resource consumption is depicted due to the number of slices (the parameters for simulation listed in table \ref{table:1} and also we set $w_C = 320$, $w_S = 100$, $w_M =1$). In this simulation, suppose the number of DCs is entirely enough to cover all slices and also, the designed parameter $\nu$ is assumed to be low, so we focused on the first term of \eqref{eqpsi}. However, if any slice remains, it can be served by more than one DCs. The optimality of the placement of DCs to slices is measured based on the power consumption of DCs. It is shown that how much resources of active DCs are not used. For ten slices, the difference between the optimal solution and the proposed solution is about $15$ percent.

>>>>

\begin{abstract}
Open radio access network (ORAN) alliance which has been formed recently establishes a flexible,  open, and smart radio access network (RAN) by combing the ideas from xRAN and cloud RAN (C-RAN). ORAN divides the functions of the RAN into three parts, namely remote unit (RU), distributed unit (DU), and central unit (CU). While RU contains lower PHY functions, DU contains higher PHY, MAC, and RLC and CU contains RRC, PDCP, and SDAP. CU and DU are implemented as virtual network functions (VNFs) running on a cloud environment. Interfaces between RU, CU, and DU are open standard interfaces. Network slicing as a new concept in 5G systems is used to share the network resources between various services while the operation of one service does not affect another service. In this paper, we study the problem of RAN network slicing in an ORAN system.  We formulate the problem of wireless link scheduling, mapping the slices to the services, and mapping the physical data centers resource to slices. The objective is to jointly maximize the energy efficiency and minimize power consumption of RUs and the cost of physical resources in a downlink channel. The problem is formulated as a mixed-integer optimization problem that can be decomposed into two independent sub-problems. Heuristic algorithms are proposed for each of the sub-problems.
\end{abstract}

\begin{IEEEkeywords}
Open RAN (ORAN), network slicing, energy efficiency.
\end{IEEEkeywords}

@@

ORAN virtualizes the elements of the radio access networks, separates them and defines appropriate open interfaces for connection of these elements. Moreover, ORAN uses machine learning techniques to develop smarter RAN layers in its architecture. In an innovative ORAN system, the programmable RAN software is decoupled from hardware \cite{oran1}. Open interface is one of the most crucial properties for ORAN to enable mobile network operators (MNOs) to define their own services.
The concept of software defined network (SDN), which is the separation of control plane from user plane, is deployed in an intelligent ORAN architecture. Moreover, this separation promotes RRM to use non-realtime (RT) and near-realtime (NRT) RAN Intelligent Controller (RIC).
In the ORAN architecture, distributed unit (DU) is a logical node having RLC/MAC/High-PHY layer.
Moreover, central unit (CU) is a logical node having RRC, SDAP and PDCP. Also, radio unit (RU) is a logical node having LOW-PHY layer and
RF processing \cite{oranpaper}.
ORAN introduces interfaces such as open fronthaul interface that connects DU and RU (i.e., E2 interface), and an A1 interface between orchestration/NMS layer containing the non-real-time RIC (RIC non-RT) function and the eNB/gNB containing the near-real-time RIC (RIC near-RT) function.

To evolve servicing in 5G networks, separation of elements of software and hardware of network is employed and referred to as network functions virtualization (NFV). Virtual network functions (VNFs) are functional blocks of the system. 5G networks are expected to host several services with different requirements simultaneously. Network slicing is considered as a solution for such demand. A network slice is a logical end-to-end network which provides service with specific requirements. Multiple network slices run on the same network infrastructure which are managed and operated independently \cite{lee2018dynamic}. Slicing can be defined for the RAN, for the core network or both of them \cite{ns1}.

Based on their type of service request, user equipments (UEs) are classified into various services, where UEs in the same service have similar service requests. In addition, each service is mapped to one or more slices based on the resources of the slices. Each VNF of the ORAN is mapped to one or more virtual machines (VMs) in the data center. For simplicity of analysis and without loss of generality, we assume a VNF is mapped to one VM and requires specific physical resources including storage, memory, and processing \cite{frdl,luong2018novel,luong2018novel1}.

%The compression of messages passed through the fronthaul link due to the limited capacity of these links is considered in \cite{simeone2016cloud,1111}.
In \cite{oranT},  the evolution of RAN in the  5G network is described. The architecture of C-RAN and xRAN is expressed and development of the ORAN from C-RAN and xRAN is explained. Also requirements of the network in terms of capacity and latency is taken into account.
In \cite{oran12},  the ORAN architecture is studied. The eight working groups are discussed including: focus areas of ORAN alliance which contains use-cases, overall architecture,  open interfaces, and  the virtualization and modularization of hardware and software. To the best of our knowledge, there is not work in the literature to model ORAN systems.

@@

In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The RAN is divided into three layers including RU, DU, and CU with open interfaces. DU and CU are running on general purpose data centers. UEs are divided to different services according to their requirements. RAN resources are partitioned into slices to provide requirements of services. Optimal power allocation and joint mapping of slices to services are applied. In addition, mapping slices to physical resources is taken into account. The contributions of the paper are as follows:
\begin{itemize}
\item Joint network slicing and resource allocation is considered in an ORAN system.
\item We formulate the problem of assigning UEs to services, services to slices, and physical wireless and data center resources to the slices as an optimization problem.
\item Novel heuristic algorithms are applied for these sub-problems to efficiently obtain the solution.
\end{itemize}

The rest of the paper is organized as follows. In Section \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical data center resources is introduced. Then, problem statement is explained and decomposed into two independent sub-problems.
In Section \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In Section \ref{simul}, numerical results are provided to investigate the performance of the algorithms.

@@

single-antenna UEs that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ physical resource blocks (PRBs), one DU and one CU that contains VNFs.
Slices can have shared resources. All RUs in a slice, that are mapped to a service, transmit signals cooperatively to all the UEs in a specific service \cite{motalleb2017optimal,mimoCran}. Each RU $r \in \{1,2,...,R \}$ is mapped to a DU via an optical fiber link with limited fronthaul capacity.

@@

Also, RUs and PRBs can serve more than one slice.

@@

Mean delay of each slice is obtained as below.

@@

where, $P_r^{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RUs in all slices. Also, $\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the total rates of all UEs applied for all types of services.

@@

\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{Y} }   \quad &  \eta(\boldsymbol{P},\boldsymbol{A})+ \varphi \frac{1}{\psi_{tot}(\boldsymbol{Y})} \\

@@

Also, $\varphi$ is weighted variable to value between first and second term of objective function.

@@

\If {conditions \eqref{c11}, \eqref{c12}, \eqref{c13} and \eqref{c14} are not applied}

@@

\caption{Placement of Physical resources into Virtual resources}\label{alg3}

@@

In this section, numerical results for the main problem are depicted.

@@

 Maximum transmit Power of each RU & 40dBm \\

@@

In Fig. \ref{fig:f1a}, energy efficiency is depicted for two different numbers of services with different mean number of UEs in each service. The parameters of simulations are listed in Table \ref{table:1a}. The optimal method is obtained by using MOSEK toolbox to obtain $\boldsymbol{A}$ and CVX toolbox to obtain $\boldsymbol{P}$. They iteratively update $\boldsymbol{A}$, $\eta$ and $\boldsymbol{P}$. The optimal method is $0.1$ bits/J/Hz better than the proposed method for $V = 6$ and $E[U_v] = 10$, and also, $0.09$ bits/J/Hz better than the proposed method for $V = 3$ and, $E[U_v] = 10$. As it is shown, the energy efficiency is increased as mean number of UEs rises.

@@

In Fig. \ref{fig:f1}, the ratio of admitted slices is demonstrated for two different numbers of DCs with the different number of slices. The parameters of the simulation are listed in Table \ref{table:1}. We also set $w_C = 320$, $w_S = 100$, $w_M =1$. In this simulation, the second term of \eqref{eqpsi}, is important and the designed parameter $\nu$ is supposed to be high.

@@

The proposed method is based on Algorithm \ref{alg3}, and the optimal method is obtained using MOSEK toolbox.

@@

In Fig. \ref{fig:f2}, the normalized resource consumption is depicted versus the number of slices. The parameters for simulation are listed in Table \ref{table:1}. We also set $w_C = 320$, $w_S = 100$, $w_M =1$). In this simulation, suppose the number of DCs is entirely enough to cover all slices and the designed parameter $\nu$ is assumed to be low, so we focused on the first term of \eqref{eqpsi}. However, if any slice remains, it can be served by more than one DCs. The optimality of the placement of DC resources to slices is measured based on the power consumption of DCs. It is shown the amount of resources of DCs which are not used. For ten slices, the difference between the optimal solution and the proposed solution is about $15$ percent.
